### 2011-04-18 paper_gecco_2/abstract.tex
Cut 8 page version to 2 pages. 1:42:49 :)

Creating gaits for legged robots is an important task to enable robots
to access rugged terrain, yet designing such gaits by hand is a
challenging and time-consuming process. In this paper we investigate
various algorithms for automating the creation of quadruped
gaits. Because many robots do not have accurate simulators, we test
gait learning algorithms entirely on a physical robot.  We compare the
performance of two classes of learning gaits: locally searching
parameterized motion models and evolving artificial neural networks
with the HyperNEAT generative encoding. Specifically, we test six
different parameterized learning strategies: uniform and Gaussian
random hill climbing, policy gradient reinforcement learning,
Nelder-Mead simplex, a random baseline, and a new method that builds a
model of the fitness landscape with linear regression to guide further
exploration.  While all parameter search methods outperform a
manually-designed gait, only the linear regression and Nelder-Mead
simplex strategies outperform a random baseline strategy. Gaits
evolved with HyperNEAT perform considerably better than all
parameterized local search methods and produce gaits nearly 9 times faster than a hand-designed gait.  The best HyperNEAT gaits exhibit
complex motion patterns that contain multiple frequencies, yet are
regular in that the leg movements are coordinated.

>>>>

Creating gaits for legged robots is an important task to enable robots
to access rugged terrain, yet designing such gaits by hand is a
challenging and time-consuming process. In this paper we investigate
various algorithms for automating the creation of quadruped
gaits. Because many robots do not have accurate simulators, we test
gait learning algorithms entirely on a physical robot.  We compare the
performance of two classes of learning gaits: locally searching
parameterized motion models and evolving artificial neural networks
with the HyperNEAT generative encoding.  All parameter search methods
outperform a manually-designed reference gait, but HyperNEAT performs
better still, producing gaits nearly 9 times faster than the reference
gait.

### 2011-04-18 paper_gecco_2/platformDetails.tex
Cut 8 page version to 2 pages. 1:42:49 :)

All of the computation for gait learning, fitness evaluation, and
robot control was performed on the compact on-board CompuLab Fit-PC2,
running Ubuntu Linux.  All gait generation, learning, and fitness
evaluation code, except HyperNEAT, was written in Python and is
available on our website \cite{quadratotWeb}.  HyperNEAT is written in
C++.  We controlled the servos with the \code{pydynamixel} library
\cite{pydynamixel}.  The robot connected to a wireless network on
boot, which enabled us to control it via SSH.

>>>>

All of the computation for gait learning, fitness evaluation, and
robot control was performed on the compact on-board CompuLab Fit-PC2,
running Ubuntu Linux.  All gait generation, learning, and fitness
evaluation code, except HyperNEAT, was written in Python and is
available on our website (http://bit.ly/geccogait).  HyperNEAT is written in
C++.  We controlled the servos with the \code{pydynamixel} library
\cite{pydynamixel}.  The robot connected to a wireless network on
boot, which enabled us to control it via SSH.
